%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Final-year Internship, Digital Power Optimization} % Job title
    {NXP Semiconductors} % Organization
    {Nice (Sophia Antipolis), France} % Location
    {March. 2016 - Exp. Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Working on power consumption optimisation on the digital part of a mixed signal IC (Audio Amplifier).}
	\item { Gate level simulation and TCF dumping for power comsumption analysis, indentification of power bugs and huge power wastage of different blocks on the design.}
	\item {Exploring power saving opportunity, clock gating insertion, implementation of Self gating technique on blocks with asynchronious events.}
	\item {implementation of Dynamic frequency scaling (DFS) based on running mode of the circuit. }
	\item {Low Power synthesis and logic equivqlence checking after RTL update.}
	\item {study of advanced power reduction techniques such as PSO, DVFS, Power partitioning...}
        \item {Agressive power reduction using common Power Format (CPF) on the design flow.}
	\item {Possible change of the PLL IP and redesign clock deviders on the CGU.}
	\item {Tools Used : Cadence..., Power-Artist.}
	\item {Environement: Linux (Redhat), VHDL, VERILOG, TCL.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Summer Intern (RTL Designer)} % Job title
    {LIP6 Center for Scientific Research} % Organization
    {Paris, France} % Location
    {June. 2015 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Study and profiling of a SystemC (CABA) model of a VCI AHCI SDCard controller component.}
	\item {Description, modeling and implementation with VHDL as part of the TSAR project.}
	\item {Functional verification, cosimulation (SystemC/VHDL) using ModelSim in a virtual prototype architecture with Soclib components and the GIET\_VM operating system.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
